A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-09 dl-paper.tex
Fix misprint
Minor

The authors would like to express their gratitude to A.~Stavrova for posing the problem and also to A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.

@@

From the second property we also immediately obtain the following group factorization.
\begin{corollary} For $\Phi$ as above one has $\E(\Phi, A[X] + M[X\inv]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).$ \end{corollary}

>>>>

The authors would like to express their gratitude to A.~Stavrova, A.~Stepanov and N.~Vavilov for their useful comments and interest in this work.

@@

From the second property we also immediately obtain the following group factorization.
\begin{corollary} For $\Phi$ as above one has $\E(\Phi, A[X\inv] + M[X]) = \E(\Phi, A[X], M[X]) \cdot \E(\Phi, A[X\inv]).$ \end{corollary}
